\Title

### 2020-02-18 manuscript/manuscript.tex
Start writing Synthetic Model section

\documentclass[twocolumn]{article}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[round]{natbib}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}

@@

The synthetic model is made out of \textbf{number} number of prisms distributed
on a region of 100km$\times$100km between 10km deep and surface level.

>>>>

\documentclass[twocolumn]{article}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[round]{natbib}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}

@@

The synthetic model is made out of \textbf{number} number of prisms distributed
on a region of \SI{100}{\km}$\times$\SI{100}{\km} between \SI{10}{\km} deep and
the zero height plane.
Density of prisms range from \SI{-900}{\kg\per\cubic\m} and
\SI{500}{\kg\per\cubic\m}.
We created deep big and thin shallow prisms for creating gravity anomalies with
long and short wavelengths, respectively.

The gravitational effect of the synthetic model has been computed on a regular
grid of 56$\times$57 points with a spacing of \SI{2}{\km} located
\SI{2000}{\m} above the zero height plane (Fig.~\ref{fig:target-grid}).
We will refer to this grid as the \emph{target} grid in the future.

\begin{figure*}
    %\includegraphics[width=\linewidth]{}
    \caption{
        Target grid. Gravitational effect of synthetic model on a regular grid
        composed of 56$\times$57 points with a spacing of \SI{2}{\km} located
        \SI{2000}{\m} above the zero height plane.
    }
    \label{fig:target-grid}
\end{figure*}
